`{peacesciencer}`:  A User’s  Guide  for  Quantitative  Peace Science in R

### 2021-06-10 user-guide/ms.Rmd
meh

---
title: "`{peacesciencer}`:  A User’s  Guide  for  Quantitative  Peace Science in R"
thanks: "Replication files are available on the author's Github account (https://github.com/svmiller/peacesciencer). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
author:
- name: Steven V. Miller
  affiliation: Clemson University
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
# bibliography: inst/refs.bib
abstract: "This article introduces `{peacesciencer}`, an R package that contains a litany of tools for creating data of widespread interest to the peace science community. The package is cross-platform, assuming only a recent installation of the R programming language with some of the enhanced functionality of the broadly popular `{tidvyerse}` packages. Peace science researchers can use this package to greatly reduce the time needed to perfectly recreate dyad-year and state-year data from scratch and merge in common indicators included in almost every dyad-year or state-year analysis (e.g. democracy data, contiguity data). The software is freely available on CRAN and maintains an active website documenting its features at http://svmiller.com/peacesciencer."
keywords: "software, statistical analysis, peace science, reproducibility"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
alwaays_allow_html: TRUE
header-includes:
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
  - \usepackage{colortbl}
  - \arrayrulecolor{black}
#  - \midrule\relax
---

@@

Fifth, statistical software should be kind to graduate students in peace science with the aforementioned point in mind. Graduate students just beginning their career in peace science scholarship are tasked to learn the substantive material, the characteristics of the underlying data in wide use in the community, and the quantitative methods and statistical software available to them, effectively all at the same time. A student interested in civil conflict scholarship will need to learn the UCDP-PRIO armed conflict data in some detail at the same time they learn about the theoretical arguments that informed the creation of the data, likely at the same time they take quantitative methods courses that show them how to load and explore data in a choseen statistical software. At the same time that creating data is increasingly blurred with coding and processing data, students are simultaneously learning to explore data for themselves as they read about the analyses of the data. `{peacesciencer}` aims to make this process easier for graduate students using the features of the R programming language. Graduate students can use `{peacesciencer}` to learn about peace science data and computer programming in R at the same time.

>>>>

---
title: "`{peacesciencer}`:  A User’s  Guide  for  Quantitative  Peace Science in R"
thanks: "Replication files are available on the author's Github account (https://github.com/svmiller/peacesciencer). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
author:
- name: Steven V. Miller
  affiliation: Clemson University
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
# bibliography: inst/refs.bib
abstract: "This article introduces `{peacesciencer}`, an R package that contains a litany of tools for creating data of widespread interest to the peace science community. The package is cross-platform, assuming only a recent installation of the R programming language with some of the enhanced functionality of the broadly popular `{tidvyerse}` packages. Peace science researchers can use this package to greatly reduce the time needed to perfectly recreate dyad-year and state-year data from scratch and merge in common indicators included in almost every dyad-year or state-year analysis (e.g. democracy data, contiguity data). The software is freely available on CRAN and maintains an active website documenting its features at http://svmiller.com/peacesciencer."
keywords: "software, statistical analysis, peace science, reproducibility"
geometry: margin=1in
csl: inst/jpr.csl
mainfont: cochineal
#sansfont: Linux Biolinum O 
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
alwaays_allow_html: TRUE
header-includes:
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
  - \usepackage{colortbl}
  - \arrayrulecolor{black}
#  - \midrule\relax
---

@@

Fifth, statistical software should be kind to graduate students in peace science with the aforementioned point in mind. Graduate students just beginning their career in peace science scholarship are tasked to learn the substantive material, the characteristics of the underlying data in wide use in the community, and the quantitative methods and statistical software available to them, effectively all at the same time. A student interested in civil conflict scholarship will need to learn the UCDP-PRIO armed conflict data in some detail at the same time they learn about the theoretical arguments that informed the creation of the data, likely at the same time they take quantitative methods courses that show them how to load and explore data in a chosen statistical software. At the same time that creating data is increasingly blurred with coding and processing data, students are simultaneously learning to explore data for themselves as they read about the analyses of the data. `{peacesciencer}` aims to make this process easier for graduate students using the features of the R programming language. Graduate students can use `{peacesciencer}` to learn about peace science data and computer programming in R at the same time.
